Palomar 5 Gaps

### 2024-09-17 paper/main.tex
added figure links

      The core of our analysis is presented in Fig.~XXX. The bottom panel shows the evolution of the stream density over time. To avoid extreme low-density regions at the stream's edges, we applied a density threshold to focus on the more significant areas of the stream. Next, we modeled Palomar 5's orbit as a proxy for its stream and sampled points along the orbit to measure the gravitational force exerted by other globular clusters. This force data is displayed in the top panel of Fig.~XXX, showing how the total gravitational acceleration on Palomar 5's stream evolves over its length throughout the simulation.

@@

      The results of this analysis were compiled into a table. If a gap was attributed to a particular globular cluster, it was labeled as \texttt{TRUE}; otherwise, it was marked as \texttt{FALSE}. For a handful of simulations, to double check that the verdict made correctly when passing from suspect to culprit, we re-compute the simulations yet individually adding one globular cluster at a time. As a result, we are able to confirm that singular gaps arrise from the suspected clusters.

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{force_on_orbit-monte-carlo-009.png}
    \caption[]{This figure demonstrates how we determined which globular clusters were responsible for the gaps. The bottom plot showcases the evolution of the stream density in simulation time. The y-axis is $\tau$, which is a coordinate in units of time that indicates how far ahead or behind it is from a globular cluster. The x-axis is the simulation time, $t$, where 0~s km~kpc$^{-1}$ indicates present time. The density was used to determine a sutible length of the stream as a function of time. This length was then used to extract a piece of Palomar 5's orbit about a given position of Pal 5 in time. This orbital segment is used to approximate the stream. Then, the gravitational force from all other clusers was computed on the orbit. Moments of high acceleration indicate the passage of another cluster. The top 5 strongest passages are labeled with red circles as well as the name of the clusters. }
    \label{fig:profiles}
    \end{figure*}

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{decomposition-monte-carlo-009-with-3-gaps.png}
    \caption[]{This figure decomposes the gaps found in the full simulation to the responsible perturbers. The pertuber candidates were found in Fig.~\ref{fig:profiles}, and extra simulations were run in which we singularly add the suspects to verify that it was indeed them who created the gaps. The titles explain which simulation is which, and there's also a descrepandy map. (I think I'm going to get rid of the DIFF map)}
    \label{fig:profiles}
    \end{figure*}

>>>>

      The core of our analysis is presented in Fig.~\ref{fig:force-on-orbit}. The bottom panel shows the evolution of the stream density over time. To avoid extreme low-density regions at the stream's edges, we applied a density threshold to focus on the more significant areas of the stream. Next, we modeled Palomar 5's orbit as a proxy for its stream and sampled points along the orbit to measure the gravitational force exerted by other globular clusters. This force data is displayed in the top panel of Fig.~\ref{fig:force-on-orbit}, showing how the total gravitational acceleration on Palomar 5's stream evolves over its length throughout the simulation.

@@

      The results of this analysis were compiled into a table. If a gap was attributed to a particular globular cluster, it was labeled as \texttt{TRUE}; otherwise, it was marked as \texttt{FALSE}. For a handful of simulations, to double check that the verdict made correctly when passing from suspect to culprit, we re-compute the simulations yet individually adding one globular cluster at a time. As a result, we are able to confirm that singular gaps arrise from the suspected clusters, an example of which is shown in Fig.~\ref{fig:decomposition}.

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{force_on_orbit-monte-carlo-009.png}
    \caption[]{This figure demonstrates how we determined which globular clusters were responsible for the gaps. The bottom plot showcases the evolution of the stream density in simulation time. The y-axis is $\tau$, which is a coordinate in units of time that indicates how far ahead or behind it is from a globular cluster. The x-axis is the simulation time, $t$, where 0~s km~kpc$^{-1}$ indicates present time. The density was used to determine a sutible length of the stream as a function of time. This length was then used to extract a piece of Palomar 5's orbit about a given position of Pal 5 in time. This orbital segment is used to approximate the stream. Then, the gravitational force from all other clusers was computed on the orbit. Moments of high acceleration indicate the passage of another cluster. The top 5 strongest passages are labeled with red circles as well as the name of the clusters. }
    \label{fig:force-on-orbit}
    \end{figure*}

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{decomposition-monte-carlo-009-with-3-gaps.png}
    \caption[]{This figure decomposes the gaps found in the full simulation to the responsible perturbers. The pertuber candidates were found in Fig.~\ref{fig:profiles}, and extra simulations were run in which we singularly add the suspects to verify that it was indeed them who created the gaps. The titles explain which simulation is which, and there's also a descrepandy map. (I think I'm going to get rid of the DIFF map)}
    \label{fig:decomposition}
    \end{figure*}
